Concurrent Programming in Harmony

### 2022-01-28 book/paper.tex
typo in book
Added OpSave to TLA+ spec

Method <{wait}> adds the context of the thread---used as a unique
identifier for the thread---to the bag,
incrementing the number of threads in the bag with the same context.
The Harmony <{save}> expression (\autoref{ap:context}) returns a tuple
containing a value (in this case `<{()}>' and the context of the thread.
<{wait}> then loops until that count is restored to the
value that it had upon entry to <{wait}>.
Method <{notify}> removes an arbitrary context from
the bag, allowing one of the threads with that context to
resume and re-acquire the lock associated with the monitor.
<{notifyAll}> empties out the entire bag, allowing all threads
in the bag to resume.

@@

The <{stop p}> expression stores the context of the thread right after
the expression in <{!p}> (i.e., <{p}> must be an address value) and
terminates the thread.  The thread can later be reinstantiated with
<{go !p r}>, in which case the <{stop}> expression returns <{r}>.
A thread can be for ever suspended using <{stop None}>.

>>>>

Method <{wait}> adds the context of the thread---used as a unique
identifier for the thread---to the bag,
incrementing the number of threads in the bag with the same context.
The Harmony <{save}> expression (\autoref{ap:context}) returns a tuple
containing a value (in this case `<{()}>') and the context of the thread.
<{wait}> then loops until that count is restored to the
value that it had upon entry to <{wait}>.
Method <{notify}> removes an arbitrary context from
the bag, allowing one of the threads with that context to
resume and re-acquire the lock associated with the monitor.
<{notifyAll}> empties out the entire bag, allowing all threads
in the bag to resume.

@@

The <{stop p}> expression stores the context of the thread right after
the expression in <{!p}> (i.e., <{p}> must be an address value) and
terminates the thread.  The thread can later be reinstantiated with
<{go !p r}>, in which case the <{stop}> expression returns <{r}>.
A thread can be for ever suspended using <{stop None}> or just <{stop()}>.
